% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Scholarships and additional info
\sectionTitle{Education}{\faMortarBoard}

\begin{experiences}
\consultantexperience
    {February 2019}   {Doctor in Engineering}{Universidade Tecnológica Federal do Paraná}{Curitiba}
    {March 2015} {One-year Sandwich Period in the Operations Research and Logistics group, in Wageningen University and Research (WUR)}{}
                    {
                      \begin{itemize}
                        \item Thesis Title: Design of Regenerative Supply Networks      \item Supervisors: Prof.dr. Milton Borsato, Prof.dr.ir. Jacqueline Bloemhof.        
                      \end{itemize}
                   } {Regenerative Design, Transdisciplinarity, Optimization}
\emptySeparator   
\acaexperience
    {June 2012}   {MSc. in Engineering}{Universidade Tecnológica Federal do Paraná}{Curitiba}
    {March 2010} {
                    \begin{itemize}
                        \item Dissertation Title: Combining Stage-Gate\textsuperscript{TM} and Set-Based engineering in a product assessment tool focused on sustainable end-of-life
                        \item Supervisor: Prof.dr. Milton Borsato.        
                   \end{itemize}
                      }{set-based design, stage-gate, sustainable end-of-life}  
\emptySeparator   
\experience
    {December 2006}   {Bachelor's in Mechanical Engineering}{Universidade Federal do Paraná}{Curitiba}
    {March 2001} {\begin{itemize}
        \item Agrogas: general considerations on target audience and end-user suitability 
        \item Supervisor: Prof.dr. Maria José de Santana Ponte
    \end{itemize}
                      
                   }
\end{experiences}

\begin{scholarship}
	\scholarshipentry{}{\textsc{\textbf{Other Courses}}}
	\scholarshipentry{2017}
					{Modelling and Simulation of Complex Socio-Technical Systems (INF-51806): 90h course - Wageningen University and Research, The Netherlands.}
	\scholarshipentry{}
					{8\textsuperscript{th} ESSA / SiLiCo Summer School in Social Simulation: “Agent-based modelling for resilience”: 36h course - Wageningen University and Research, The Netherlands.}
	\scholarshipentry{}
					{Biobased Logistics (ORL-32306): 49h course - Wageningen University and Research, The Netherlands.}
	\scholarshipentry{2006}
					{Working Managerial Competences: 48h training - Dale Carnegie Institute, Brazil.}
	\scholarshipentry{2004}
					{MSA - Measurement System Analysis: 12h training - ATSG – Porto Alegre, Brazil.}
	\scholarshipentry{}
					{FMEA - Failure Mode and Effect Analysis: 8h training - ATSG – Porto Alegre, Brazil.}
	\scholarshipentry{}
					{APQP - Advanced Product Quality Planning: 16h training - ATSG – Porto Alegre, Brazil.}
\end{scholarship}