%%
% German Latex Letter Template 
% Use if you want to crate a Letter in DIN A4. You can use it in English and German 
% as well, just set language at begining of plain text.
% Created by Jan Boelmann @ Nov. 2016 Jan.boelmann@live.de
%%

\documentclass[sender,
    paper=a4,
    version=last,
    fontsize=12pt,
    DIV=12,
    BCOR=0mm]{scrlttr2}
\parskip3mm
\parindent0mm % if you want to have no lineskip
\usepackage[english,ngerman]{babel}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}

% Set Font: sans serif Latin Modern
\usepackage{lmodern}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

% Set Page layout:
\usepackage{changepage}
%\changepage{text height}{text width}{even-side margin}
%{odd-side margin}{column sep.}
%{topmargin}{headheight}{headsep}{footskip}
\changepage{+3cm}{}{}{}{}{}{}{}{-5cm}
\LoadLetterOption{sender}

\begin{document}
% Set Appendix text at very end (dubble point will be set automatically)
\setkomavar*{enclseparator}{Appendix}
% subject, date, place:
%\setkomavar{subject}{On becoming an Assistant Professor of Sustainable Complex Adaptive Systems}
\selectlanguage{english}
\setkomavar{date}{\today}
\setkomavar{place}{Cornélio Procópio}

% Set recipient of letter
\begin{letter}{
    Prof.dr.ir. Ivo J.B.F. Adan \\
    Eindhoven University of Technology (Tu/e)\\
    PO Box 513, \\
    5600 MB Eindhoven, The Netherlands
} 

\opening{Dear Prof.dr.ir. Adan,}

% Write here your Letter text. You can choose here the language for typeset. ("english", or "ngerman")

\parindent8mm

I am writing to apply for the position of Assistant Professor in Operations Management (REF.: V39.4656) because I see it as an invaluable, exciting opportunity for many reasons. 

I have been performing research on Sustainable Operations Management since 2011, 

after watching Prof. Carl Folke's lecture in Wageningen. Two of his propositions stunned me: "technological solutions cannot solve cultural problems" - so controversial! -, and "governance is not government". 

What do I want to do for research in sustainable operations management? Ver figura no Evernote

Besides research, I have practical experience with operations management. I spent five years in the automotive industry, leading multidisciplinary groups through the design and development of mechanical parts. I reported project updates to board meetings and followed customers' requirements. In 2010, I changed my focus to academia, and discovered a passion for sustainable development. For my Master's, I developed a conceptual model for sustainable product development, focused on end-of-life. Later, I spent four fruitful years of my PhD: in Wageningen, I followed two courses promoted by Prof. Hofstede on Complex Adaptive Systems, and one course on Biobased Logistics. For my PhD. thesis, I modelled a business process to design eco-effective supply chains. I also explored using the Ecosystem Network Analysis, a model based on information theory implemented in R, as a metric for Resilience. Finally, I proposed a metaphor for Regenerative Supply Networks, upon which I designed a restorative household waste management system. I used Vensim to create a stock and flows model, using its output in an optimisation model developed in XPress IVE. 

In my future research, I intend to model ... the emergence of behavioural change and social interactions to accelerate the transition to a more sustainable society. 

This is not my only passion, however: I am also enthusiastic about academic duties. In 2014, I led the implementation of the Academic Department of Mechanics of the campus I work, and conducted a successful restructure of the bachelor's in Mechanical Engineering. For the past two years now, I have been increasingly adopting active learning in my courses. Adapting teaching activities have been pretty challenging, especially after COVID-19 outbreak: students are much accustomed to expository teaching, still widely used by most professors. Nevertheless, I am receiving satisfactory feedback from the students, and to observe how they develop soft and hard skills inspires me to keep developing my skills in active learning. 

Achieving a sustainable society in the long term is a personal ambition. I can add substantial value through my solid background on mechanical engineering, my experience with design and development and multi-level analysis. I'm confident I can help the Operations, Planning, Accounting \& Control group to make a substantial contribution to research and practice, using my modelling and communication skills and my ability to propose comprehensive, creative solutions. I’m looking forward to discussing the position with you, and I remain available to provide you with any additional information you might need.

%\selectlanguage{english}%Choose language for closing text
\closing{With kind regards,} % use "Mit freundlich Grüßen" i.e. 
\vfill
\encl{\small{Detailed CV with References; Research and Teaching Statement; Sustainable Design Portfolio.}}
% end of letter
\end{letter}

\end{document}

