\section*{Research Statement}
\vspace{-8pt}

%INTRO

"Technological solutions cannot solve cultural problems", stated Carl Folke, in a lecture I had the priviledge to attend in Wageningen in 2017. Technology plays an essential role for problem solving, but it must be regarded as one dimension among the many to be considered while proposing solutions. Since my early days in the Automotive Industry, my interests have been shifting from technology-oriented Mechanical Engineering towards Social Sciences and Complex Adaptive Systems. 

%past and present

In the past, I performed prescriptive researach, developing artefacts to design out waste and pollution, increase circularity of materials and regenerate the environment \cite{EllenMacArthurFoundation2015} using Design Science \cite{VanAken2004,Peffers2007a}. I became enthusiastic to advance Sustainable Development in the field of Operations Management. Today, I see myself as a creative, fast-learning \textbf{Sustainable Systems Engineer}, wielding "a net of methodologies" \cite{self1978}, with the purpose of closing the resource circularity gap \cite{CircleEconomy2020b}. 

%present and future

Currently, I continue demonstrating how the circularity gap can be minimised through the research project \textbf{ReCircleNet}, where resource circularity networks are identified, their contributions for sustainable development quantified and their evolution  simulated. For the future, my ambitions in research are related with a methodological approach and two practical problems related with flows.  

The methodological approach is called \textbf{Design for Emergence}, and it consists in creating the environmental conditions needed for the system to emerge - a bottom-up approach where agents self-organise the way they see fit, rather than a top-down, normative design, which is likely to create unforeseen problems. For such approach, modelling paradigms like System Dynamics and Agent-based Modelling are combined, and scenarios are simulated to verify the outcomes achieved out of the environmental conditions modified.

The problems I aim to contribute solving are related with flows: the material flows - mainly waste flows - and the people flows, i.e., mobility flows...
